The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-17 paper/Analisis.tex
small edits in the analysis section

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
%\bibliographystyle{apj}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

%\documentclass[usenatbib]{mn2e} 
%\usepackage{amsmath} 
%\usepackage{amssymb} 
%\usepackage{graphics}
%\usepackage{graphicx}
%\usepackage{epsfig} 
%\usepackage{float} 
%\def\be{\begin{equation}}
%\def\ee{\end{equation}}
%\def\ba{\begin{eqnarray}}
%\def\ea{\end{eqnarray}}
%\bibliographystyle{mn2e}
% To highlight comments 
%\usepackage{color}
%\definecolor{red}{rgb}{1,0.0,0.0}
%\newcommand{\red}{\color{red}}
%\definecolor{blue}{rgb}{0.1,0.3,0.9}
%\newcommand{\blue}{\color{blue}}

%\usepackage[normalem]{ulem}
%\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
%\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
%\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
%\newcommand{\LCDM}{$\Lambda$CDM~}
%\newcommand{\beq}{\begin{eqnarray}}  
%\newcommand{\eeq}{\end{eqnarray}}

%\newcommand{\zz}{$z\sim 3$} 
%\newcommand{\apj}{ApJ}  
%\newcommand{\apjs}{ApJS}  
%\newcommand{\apjl}{ApJL}  
%\newcommand{\aj}{AJ}  
%\newcommand{\mnras}{MNRAS}  
%\newcommand{\mnrassub}{MNRAS accepted}  
%\newcommand{\aap}{A\&A}  
%\newcommand{\aaps}{A\&AS}  
%\newcommand{\araa}{ARA\&A}  
%\newcommand{\nat}{Nature}  
%\newcommand{\physrep}{PhR}
%\newcommand{\pasp}{PASP}    
%\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

@@

Following the classification of $Ly\alpha$ profiles made for (Kulas et al, put reference) 
we divide our results in $3$ different groups. Group I represents profiles in which the flux in the red side 
is stronger that in the blue part, while Group II represents profiles in which the blue side
is the stronger. Group III represents single peaked profiles while Group IV represents multipeaked  
profiles.

Group I profiles may be explained in our model when off-center emission is present and the location 
of this photons emission is stronger in the , while Group II profiles correspond to emissions in the ..

@@

% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail observaciones, Kulas, YAMADA  off-center emission

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

\usepackage{graphics}
\usepackage[dvips]{epsfig}

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

@@

Gas bulk rotation has a noticeable effect on the morphology of the \ly line. In
this section we discuss the observational implications of these
findings.

We start by a quantitative discussion of the line morphology. Here we
follow  following a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger that in the blue, in Group II the blue peak is
stronger, in Group III there are single peaked profiles while while
Group IV containes multipeaked lines.

Neither Group I nor II can be explained by rotation. However, the
morphologies of the lines in Group III and IV are similar to some of
the results obtained in this paper.

@@

% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail
% observaciones, Kulas, YAMADA  off-center emission
